Every Author as First Author

### 2023-03-29 paper.tex
HTML example

Listing~\ref{lst:namestack} shows the main source code for this macro.
The main idea is to render each name (into a \TeX\ horizontal box),
and stack those boxes vertically (in a \TeX\ vertical box)
with a negative one-line vertical space in between consecutive boxes.
The example above effectively becomes:

\begin{center}
\begin{lstlisting}
\vbox{%
  \hbox{Erik Demaine}%
  \vskip-\baselineskip
  \hbox{Martin Demaine}%
}%
\end{lstlisting}
\end{center}

@@

>>>>

Listing~\ref{lst:namestack} shows the source code for this macro.
The main idea is to render each name (into a \TeX\ horizontal box),
and stack those boxes vertically (in a \TeX\ vertical box)
with a negative one-line vertical space in between consecutive boxes.
The example above effectively becomes:

\begin{lstlisting}
\vbox{%
  \hbox{Erik Demaine}%
  \vskip-\baselineskip
  \hbox{Martin Demaine}%
}%
\end{lstlisting}

@@

\lstset{
  language=HTML,
  alsoletter={-},
  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
  emph={stack, name}, % not working because of tag option
  identifierstyle=
}

We also give a proof-of-concept that the same style of rendering is
possible in HTML content.  Figure~\ref{fig:html} shows a rendering
of the HTML code in Listing~\ref{lst:html}.
CSS Grid makes implementing an overlapping stack quite easy:
by placing each name in the same grid cell,
the cell automatically grows to the maximum size of all names.

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.2]{figs/html.png}
  \caption{Rendering of HTML in Listing~\ref{lst:html}.
    Screenshot from Google Chrome 111 on Windows 11.}
  \label{fig:html}
\end{figure}

\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}

\section{Future Work}
